A secondary screen architecture to accurately capture viewers' interactions in an iTV environment

### 2014-05-29 src/paper.tex
WIP: Rewriting the introduction

TV watching is essentially a social activity, where family, friends, or people with a common interest share the same space and TV set for entertainment or information. After many advances in technologies, for interactive and digital TV, it is possible to develop high-level applications to enrich the watching experience. Thus, the interaction between viewers and TV became more elaborated than simply change channels and adjust sound volume.

The interactions between viewers and TV can be classified as implicit and explicit. Implicit interactions are part of the natural actions of watching TV (e.g., changing channels). In explicit interactions, viewers contribute by actively evaluating, commenting, or sharing their opinion about a given content. Both kinds of interaction are important for applications that rely on audience generated data.

Considering the interactions of millions of viewers, the captured data can provide valuable information for content providers (CPs)~\cite{Teixeira2010}. For example, the CPs can obtain the user ratings given to TV programs, amount of viewers, and user profiles. By using proper machine learning algorithms, CPs can infer viewers' tastes from audience data in order to deliver personalized content~\cite{Kim2012,Shin2009}. However, identifying viewers and capturing their individual interactions are still a challenging activity in the traditional TV environment, which consists of the TV and viewers interacting through a remote control (RC).

>>>>

TV watching is essentially a social activity, where family, friends, or people with a common interest share the same space and TV set for entertainment or information. After many advances in technologies, for interactive and digital TV, it is possible to develop high-level applications to enrich the watching experience. Thus, the interaction between viewers and TV became more elaborated than simply change channels and adjust sound volume. As a result, considering the interactions of millions of viewers, the captured data can provide valuable information for content providers (CPs)~\cite{Teixeira2010}.

The conventional remote control(RC) is typically used as a standard medium for viewers to interact with their TVs. However, the RC presents two notable problems: (1) to automatically identify the viewers who have possession of the RC; and (2) to capture viewers' interactions and the context in which they occur. Consequently, the whole group of viewers (e.g., a family) is handled as a single user % , rather than to the viewer in charge of the RC. As a result, the tastes that were inferred from the users in charge of the RC can be imposed on the tastes of the others.

For example, the CPs can obtain the user ratings given to TV programs, amount of viewers, and user profiles. By using proper machine learning algorithms, CPs can infer viewers' tastes from audience data in order to deliver personalized content~\cite{Kim2012,Shin2009}. However, identifying viewers and capturing their individual interactions are still a challenging activity in the traditional TV environment.
